---
title: "Individualand Combined Methods Analysis"
author: "Lauren Marazzi"
date: "10/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	fig.show = "hold",
	message = FALSE,
	warning = FALSE
)

library(dplyr)
library(caret)
library(ggplot2)
library(plotly)
library(RColorBrewer)
library(heatmaply)
library(stringr)
```

# Step1: Compute AUROC and ACC Row Sums and Median values under different weights

We identify the top methods for network structure prediction by computing the area under the receiver operating characteristic (AUROC) and accuracy (ACC) row sum and median values for each of the 28 networks. We weight these variables at 5 different ranges: 

* {Weight~AUC=1~,Weight~AUC=0~}
* {Weight~AUC=0~,Weight~AUC=1~}
* {Weight~AUC=0.5~,Weight~AUC=0.5~}
* {Weight~AUC=0.3~,Weight~AUC=0.7~}
* {Weight~AUC=0.7~,Weight~AUC=0.3~}

```{r load data}
for (sim in (1:28)){
  AUC<-read.csv(paste0("sim",sim,"/Combined_Data_onlyAUC.csv"),row.names = 1) 
  ACC<-read.csv(paste0("sim",sim,"/Combined_Data_onlyACC.csv"),row.names = 1) 

  #calculate AUC only sums and medians
  AUC_sum<-cbind(AUC$Method_name,rowSums(AUC[,-1])) %>% as.data.frame()
  colnames(AUC_sum)<-c("Method_name","Sum_of_avg_across_patients")
  AUC_sum$Sum_of_avg_across_patients<-as.numeric(AUC_sum$Sum_of_avg_across_patients)

  AUC_median<-cbind(AUC$Method_name,apply(AUC[-1], 1, median)) %>% as.data.frame()
  colnames(AUC_median)<-c("Method_name","Median_across_patients")

  write.csv(AUC_sum,paste0('sim',sim,'/Combined_data_sums_onlyAUC.csv'),quote=F)
  write.csv(AUC_median,paste0('sim',sim,'/Combined_data_median_onlyAUC.csv'),quote=F)

  #calculate ACC only sums and medians
  ACC_sum<-cbind(ACC$Method_name,rowSums(ACC[,-1])) %>% as.data.frame()
  colnames(ACC_sum)<-c("Method_name","Sum_of_avg_across_patients")
  ACC_sum$Sum_of_avg_across_patients<-as.numeric(ACC_sum$Sum_of_avg_across_patients)


  ACC_median<-cbind(ACC$Method_name,apply(ACC[-1], 1, median)) %>% as.data.frame()
  colnames(ACC_median)<-c("Method_name","Median_across_patients")

  write.csv(ACC_sum,paste0('sim',sim,'/Combined_data_sums_onlyACC.csv'),quote=F)
  write.csv(ACC_median,paste0('sim',sim,'/Combined_data_median_onlyACC.csv'),quote=F)

  #  calculate equal weights sums and medians
  AUC_half<-cbind(sapply(AUC[,-1],"*",0.5))
  ACC_half<-cbind(sapply(ACC[,-1],"*",0.5))
  equal<-cbind( AUC_half + ACC_half)


  equal_sum<-cbind(AUC$Method_name,rowSums(equal)) %>% as.data.frame()
  colnames(equal_sum)<-c("Method_name","Sum_of_avg_across_patients")
  equal_sum$Sum_of_avg_across_patients<-as.numeric(equal_sum$Sum_of_avg_across_patients)

  equal_median<-cbind(AUC$Method_name,apply(equal, 1, median)) %>% as.data.frame()
  colnames(equal_median)<-c("Method_name","Median_across_patients")


  write.csv(equal,paste0('sim',sim,'/Combined_data_equal.csv'),quote=F)
  write.csv(equal_sum,paste0('sim',sim,'/Combined_data_sums_equal.csv'),quote=F)
  write.csv(equal_median,paste0('sim',sim,'/Combined_data_median_equal.csv'),quote=F)


  #calculate 0.3 AUROC and 0.7 ACC weights sums and medians
  AUC_low<-cbind(sapply(AUC[,-1],"*",0.3))
  ACC_high<-cbind(sapply(ACC[,-1],"*",0.7))
  three_seven<-cbind( AUC_low + ACC_high)


  three_seven_sum<-cbind(AUC$Method_name,rowSums(three_seven)) %>% as.data.frame()
  colnames(three_seven_sum)<-c("Method_name","Sum_of_avg_across_patients")
  three_seven_sum$Sum_of_avg_across_patients<-as.numeric(three_seven_sum$Sum_of_avg_across_patients)

  three_seven_median<-cbind(AUC$Method_name,apply(three_seven, 1, median)) %>% as.data.frame()
  colnames(three_seven_median)<-c("Method_name","Median_across_patients")

  write.csv(three_seven,paste0('sim',sim,'/Combined_data_37.csv'),quote=F)
  write.csv(three_seven_sum,paste0('sim',sim,'/Combined_data_sums_37.csv'),quote=F)
  write.csv(three_seven_median,paste0('sim',sim,'/Combined_data_median_37.csv'),quote=F)

  #calculate 0.7 AUROC and 0.3 ACC weights sums and medianssums and medians}
  AUC_high<-cbind(sapply(AUC[,-1],"*",0.7))
  ACC_low<-cbind(sapply(ACC[,-1],"*",0.3))
  seven_three<-cbind( AUC_low + ACC_high)

  seven_three_sum<-cbind(AUC$Method_name,rowSums(seven_three)) %>% as.data.frame()
  colnames(seven_three_sum)<-c("Method_name","Sum_of_avg_across_patients")
  seven_three_sum$Sum_of_avg_across_patients<-as.numeric(seven_three_sum$Sum_of_avg_across_patients)


  seven_three_median<-cbind(AUC$Method_name,apply(seven_three, 1, median)) %>% as.data.frame()
  colnames(seven_three_median)<-c("Method_name","Median_across_patients")

  write.csv(seven_three,paste0('sim',sim,'/Combined_data_73.csv'),quote=F)
  write.csv(seven_three_sum,paste0('sim',sim,'/Combined_data_sums_73.csv'),quote=F)
  write.csv(seven_three_median,paste0('sim',sim,'/Combined_data_median_73.csv'),quote=F)
}
```

# Step2: Compute Average Row Sums and Median values under different weights

Next, we compute the average Row Sums and Median values under the 5 AUROC and ACC weights.
```{r average of sums}
patterns<-c("Combined_data_sums_onlyAUC","Combined_data_sums_onlyACC","Combined_data_sums_equal","Combined_data_sums_37","Combined_data_sums_73")

dir.create("averages")

for (pattern in patterns){
  count_files <- list.files(recursive=TRUE,pattern=paste0("^",pattern,".csv"),full.names=TRUE)
  d1<-data.frame()
  for (i in count_files) {
    # read file i as a data frame
    f <- read.csv(i,row.names = 1)
    if(length(d1) == 0){
      d1 <- f
    }else
    {
     d1$Sum_of_avg_across_patients<-d1$Sum_of_avg_across_patients+f$Sum_of_avg_across_patients
    }
  }
    d1$Sum_of_avg_across_patients<-d1$Sum_of_avg_across_patients/28
    d1$Sum_of_avg_across_patients<-d1$Sum_of_avg_across_patients/50
    d1<- d1 %>% arrange(desc(Sum_of_avg_across_patients))
    write.csv(d1,paste0("averages/Average_",pattern,".csv"),quote=F)
}


```

```{r average of medians}
patterns<-c("Combined_data_median_onlyAUC","Combined_data_median_onlyACC","Combined_data_median_equal","Combined_data_median_37","Combined_data_median_73")

for (pattern in patterns){
  count_files <- list.files(recursive=TRUE,pattern=paste0("^",pattern,".csv"),full.names=TRUE)
  count_files<-count_files[!grepl("all", count_files)]
  d1<-data.frame()
  for (i in count_files) {
    # read file i as a data frame
    f <- read.csv(i,row.names = 1)
    if(length(d1) == 0){
      d1 <- f
    }else
    {
     d1$Median_across_patients<-d1$Median_across_patients+f$Median_across_patients
    }
  }
    d1$Median_across_patients<-d1$Median_across_patients/28
    d1<- d1 %>% arrange(desc(Median_across_patients))
    write.csv(d1,paste0("averages/Average_Median_",pattern,".csv"),quote=F)
}
rm(list = ls())
```

# Step3: Generate heatmaps of Average Row Sums and Median values under different weights

To identify the top performing network methods across all 28 networks and under different weights of the AUROC and ACC, we generate a heatmap with hierarchical clustering

```{r heatmaps rowsums, message=FALSE, warning=FALSE}
pal<-rev(c("#FF0000","#000000","#031e33","#0b5394","#38761d","#ffe700","#FFFFFF"))
count_files <- list.files(path="averages",recursive=TRUE,pattern=paste0("Average_Combined"),full.names=TRUE)

d1<-data.frame()
for (i in count_files){
  f<-read.csv(i,row.names = 1)

  if(length(d1) == 0){
    d1<-f
  }
  else{
    d1<- merge(d1, f, by.x = "Method_name", by.y = "Method_name")
  }

  }


  rownames(d1)<-d1$Method_name
  colnames(d1)<-c("Method_name","AUC=0.3,ACC=0.7","AUC=0.7,ACC=0.3","AUC=0.5,ACC=0.5","AUC=0,ACC=1","AUC=1,ACC=0")
  d1<- d1 %>% select(-Method_name)
  heatmaply(d1,colors = pal,show_dendrogram = c(TRUE, FALSE),labCol=c("Weight<sub>AUC=0.3</sub>,Weight<sub>ACC=0.7</sub>","Weight<sub>AUC=0.7</sub>,Weight<sub>ACC=0.3</sub>","Weight<sub>AUC=0.5</sub>,Weight<sub>ACC=0.5</sub>","Weight<sub>AUC=0</sub>,Weight<sub>ACC=1</sub>","Weight<sub>AUC=1</sub>,Weight<sub>ACC=0</sub>"),main="Average Row Sums Value across 28 Networks",file = "heatmap_rowsums.pdf",width=800,height=1000,margins = c(40, 50)) %>%
layout(height = 900)

```


<br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br>
```{r heatmaps median, message=FALSE, warning=FALSE}

patterns<-c("Combined_data_median_onlyAUC","Combined_data_median_onlyACC","Combined_data_median_equal","Combined_data_median_37","Combined_data_median_73")

count_files <- list.files(path="averages",recursive=TRUE,pattern=paste0("Average_Median"),full.names=TRUE)

d1<-data.frame()
for (i in count_files){
  f<-read.csv(i,row.names = 1)

  if(length(d1) == 0){
    d1<-f
  }
  else{
    d1<- merge(d1, f, by.x = "Method_name", by.y = "Method_name")
  }

  }


  rownames(d1)<-d1$Method_name
  colnames(d1)<-c("Method_name","AUC=0.3,ACC=0.7","AUC=0.7,ACC=0.3","AUC=0.5,ACC=0.5","AUC=0,ACC=1","AUC=1,ACC=0")
  d1<- d1 %>% select(-Method_name)
  heatmaply(d1,colors = pal,show_dendrogram = c(TRUE, FALSE),labCol=c("Weight<sub>AUC=0.3</sub>,Weight<sub>ACC=0.7</sub>","Weight<sub>AUC=0.7</sub>,Weight<sub>ACC=0.3</sub>","Weight<sub>AUC=0.5</sub>,Weight<sub>ACC=0.5</sub>","Weight<sub>AUC=0</sub>,Weight<sub>ACC=1</sub>","Weight<sub>AUC=1</sub>,Weight<sub>ACC=0</sub>"),main="Average Median Value across 28 Networks",file = "heatmap_medians.pdf",width=800,height=1000,margins = c(40, 50))  %>%
  layout(height = 900)


```
<br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br><br>




# Step4: Generate line plots of Average Row Sums and Median AUROC and ACC values under different weights

Using our heatmaps, we see that the top combined methods of network structure prediction are BF_PFmean,  T_BCmean, T_BF_BCmean, T_BF_PF_BCmean, T_BF_PFmean, T_BFmean, T_PF_BCmean, T_PFmean. We can see how these compare to the individual methods (Tigress, BCorrU, BCohF, and PCohF) in all 28 networks individually using line plots

```{r rowsums top12 lineplot function}
create_rowsum_lineplot<-function(pattern,methods){
  count_files <- list.files(recursive=T,pattern=paste0("^",pattern),full.names=TRUE)
  d1<-data.frame()
  for (i in count_files) {
    f <- read.csv(i,row.names = 1) %>% filter(Method_name %in% methods)
    f<- cbind(f,c(rep(unlist(strsplit(i,'/'))[2],nrow(f))))
    colnames(f)[3]<-c('time_series')

    #if the counts object is empty just copy the f to m
    if(length(d1) == 0){
      d1 <- f

    } else
    {
      #if the dataframe is not empty then merge the data
      d1 <- rbind(d1,f)
    }
  }

  d1$time_series<-gsub("sim","",d1$time_series)
  d1$time_series<-str_pad(d1$time_series, 2, pad = "0")
  colnames(d1)<-c("Method","Row Sum","Network")
  d1$`Row Sum`<-d1$`Row Sum`/50

  return(d1)
}


```

```{r line plots top 12 rowsums, include=FALSE}
pal<-c("#8dd3c7","#bebada","#fb8072","#80b1d3","#fdb462","#ffed6f","#b3de69","#d9d9d9","#ffffb3","#bc80bd","#ccebc5","#fccde5")
methods<-c("BCohF","BCorrU","BF_PFmean","PCohF","T_BCmean","T_BF_BCmean","T_BF_PF_BCmean","T_BF_PFmean","T_BFmean","T_PF_BCmean","T_PFmean","Tigress")

#onlyAUC
pattern<-"Combined_data_sums_onlyAUC.csv"
d1<-create_rowsum_lineplot(pattern,methods)
p<-ggplot(d1, aes(x=Network, y=`Row Sum`,group=Method,color=Method)) + geom_line() + ggtitle("Row Sums Weight<sub>AUC=1</sub>, Weight<sub>ACC=0</sub> for Top 12 Methods across Networks")+scale_color_manual(values=pal)

p1<-ggplotly(p)
export(p1, file = "lineplot_RowSums_AUConly.pdf")
```

```{r plot 1, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot2, include=FALSE}
#onlyACC
pattern<-"Combined_data_sums_onlyACC.csv"
d1<-create_rowsum_lineplot(pattern,methods)
p<-ggplot(d1, aes(x=Network, y=`Row Sum`,group=Method,color=Method)) + geom_line() + ggtitle("Row Sums Weight<sub>AUC=0</sub>, Weight<sub>ACC=1</sub> for Top 12 Methods across Networks")+scale_color_manual(values=pal)

p1<-ggplotly(p)
export(p1, file = "lineplot_RowSums_ACConly.pdf")
```

```{r plot 2, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot3, include=FALSE}
#equal weights
pattern<-"Combined_data_sums_equal.csv"
d1<-create_rowsum_lineplot(pattern,methods)
p<-ggplot(d1, aes(x=Network, y=`Row Sum`,group=Method,color=Method)) + geom_line() + ggtitle("Row Sums Weight<sub>AUC=0.5</sub>, Weight<sub>ACC=0.5</sub> for Top 12 Methods across Networks")+scale_color_manual(values=pal)

p1<-ggplotly(p)
export(p1, file = "lineplot_RowSums_equal.pdf")
```

```{r plot 3, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot4, include=FALSE}

#AUC=0.3, ACC=0.7 weights
pattern<-"Combined_data_sums_37.csv"
d1<-create_rowsum_lineplot(pattern,methods)
p<-ggplot(d1, aes(x=Network, y=`Row Sum`,group=Method,color=Method)) + geom_line() + ggtitle("Row Sums Weight<sub>AUC=0.3</sub>, Weight<sub>ACC=0.7</sub> for Top 12 Methods across Networks")+scale_color_manual(values=pal)

p1<-ggplotly(p)
export(p1, file = "lineplot_RowSums_37.pdf")
```

```{r plot 4, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot5, include=FALSE}
#AUC=0.7, ACC=0.3 weights
pattern<-"Combined_data_sums_73.csv"
d1<-create_rowsum_lineplot(pattern,methods)
p<-ggplot(d1, aes(x=Network, y=`Row Sum`,group=Method,color=Method)) + geom_line() + ggtitle("Row Sums Weight<sub>AUC=0.7</sub>, Weight<sub>ACC=0.3</sub> for Top 12 Methods across Networks")+scale_color_manual(values=pal)
p1<-ggplotly(p)
export(p1, file = "lineplot_RowSums_73.pdf")
```

```{r plot 5, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```


```{r median lineplot function}
create_median_lineplot<-function(pattern,methods){
  count_files <- list.files(recursive=T,pattern=paste0("^",pattern),full.names=TRUE)
  d1<-data.frame()
  for (i in count_files) {
    f <- read.csv(i,row.names = 1) %>% filter(Method_name %in% methods)
    f<- cbind(f,c(rep(unlist(strsplit(i,'/'))[2],nrow(f))))
    colnames(f)[3]<-c('time_series')

    #if the counts object is empty just copy the f to m
    if(length(d1) == 0){
      d1 <- f

    } else
    {
      #if the dataframe is not empty then merge the data
      d1 <- rbind(d1,f)
    }
  }

  d1$time_series<-gsub("sim","",d1$time_series)
  d1$time_series<-str_pad(d1$time_series, 2, pad = "0")
  colnames(d1)<-c("Method","Median","Network")

  return(d1)
}


```

```{r line plots top 12 median, include=FALSE}

#onlyAUC
pattern<-"Combined_data_median_onlyAUC.csv"
d1<-create_median_lineplot(pattern,methods)
p<-ggplot(d1, aes(x=Network, y=Median,group=Method,color=Method)) + geom_line() + ggtitle("Medians Weight<sub>AUC=1</sub>, Weight<sub>ACC=0</sub> for Top 12 Methods across Networks")+scale_color_manual(values=pal)

p1<-ggplotly(p)
export(p1, file = "lineplot_Median_AUConly.pdf")
```

```{r plot 6, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot7, include=FALSE}
#onlyACC
pattern<-"Combined_data_median_onlyACC.csv"
d1<-create_median_lineplot(pattern,methods)
p<-ggplot(d1, aes(x=Network, y=Median,group=Method,color=Method)) + geom_line() + ggtitle("Medians Weight<sub>AUC=0</sub>, Weight<sub>ACC=1</sub> for Top 12 Methods across Networks")+scale_color_manual(values=pal)

p1<-ggplotly(p)
export(p1, file = "lineplot_Median_ACConly.pdf")
```

```{r plot 7, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot8, include=FALSE}

#equal weights
pattern<-"Combined_data_median_equal.csv"
d1<-create_median_lineplot(pattern,methods)
p<-ggplot(d1, aes(x=Network, y=Median,group=Method,color=Method)) + geom_line() + ggtitle("Medians Weight<sub>AUC=0.5</sub>, Weight<sub>ACC=0.5</sub> for Top 12 Methods across Networks")+scale_color_manual(values=pal)

p1<-ggplotly(p)
export(p1, file = "lineplot_Median_equal.pdf")
```

```{r plot 8, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot9, include=FALSE}
#AUC=0.3, ACC=0.7 weights
pattern<-"Combined_data_sums_37.csv"
d1<-create_median_lineplot(pattern,methods)
p<-ggplot(d1, aes(x=Network, y=Median,group=Method,color=Method)) + geom_line() + ggtitle("Medians Weight<sub>AUC=0.3</sub>, Weight<sub>ACC=0.7</sub> for Top 12 Methods across Networks")+scale_color_manual(values=pal)

p1<-ggplotly(p)
export(p1, file = "lineplot_Median_37.pdf")
```

```{r plot 9, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot10, include=FALSE}

#AUC=0.7, ACC=0.3 weights
pattern<-"Combined_data_sums_73.csv"
d1<-create_median_lineplot(pattern,methods)
p<-ggplot(d1, aes(x=Network, y=Median,group=Method,color=Method)) + geom_line() + ggtitle("Medians Weight<sub>AUC=0.7</sub>, Weight<sub>ACC=0.3</sub> for Top 12 Methods across Networks")+scale_color_manual(values=pal)

p1<-ggplotly(p)
export(p1, file = "lineplot_Median_73.pdf")
```

```{r plot 10, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```



```{r all methods rowsums and median lineplot functions, include=FALSE}

create_rowsum_lineplot<-function(pattern){
  count_files <- list.files(recursive=T,pattern=paste0("^",pattern),full.names=TRUE)
  d1<-data.frame()
  for (i in count_files) {
    f <- read.csv(i,row.names = 1)
    f<- cbind(f,c(rep(unlist(strsplit(i,'/'))[2],nrow(f))))
    colnames(f)[3]<-c('time_series')

    #if the counts object is empty just copy the f to m
    if(length(d1) == 0){
      d1 <- f

    } else
    {
      #if the dataframe is not empty then merge the data
      d1 <- rbind(d1,f)
    }
  }

  d1$time_series<-gsub("sim","",d1$time_series)
  d1$time_series<-str_pad(d1$time_series, 2, pad = "0")
  colnames(d1)<-c("Method","Row Sum","Network")
  d1$`Row Sum`<-d1$`Row Sum`/50

  return(d1)
}

create_median_lineplot<-function(pattern){
  count_files <- list.files(recursive=T,pattern=paste0("^",pattern),full.names=TRUE)
  d1<-data.frame()
  for (i in count_files) {
    f <- read.csv(i,row.names = 1)
    f<- cbind(f,c(rep(unlist(strsplit(i,'/'))[2],nrow(f))))
    colnames(f)[3]<-c('time_series')

    #if the counts object is empty just copy the f to m
    if(length(d1) == 0){
      d1 <- f

    } else
    {
      #if the dataframe is not empty then merge the data
      d1 <- rbind(d1,f)
    }
  }

  d1$time_series<-gsub("sim","",d1$time_series)
  d1$time_series<-str_pad(d1$time_series, 2, pad = "0")
  colnames(d1)<-c("Method","Median","Network")

  return(d1)
}

```


We can also plot all 26 combined and individual methods on an interactive line plot


```{r all methods line plots, include=FALSE}
#onlyAUC
pattern<-"Combined_data_sums_onlyAUC.csv"
d1<-create_rowsum_lineplot(pattern)
p<-ggplot(d1, aes(x=Network, y=`Row Sum`,group=Method,color=Method)) + geom_line() + ggtitle("Row Sums Weight<sub>AUC=1</sub>, Weight<sub>ACC=0</sub> for Top 12 Methods across Networks")

p1<-ggplotly(p)
```

```{r plot 11, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot 12, include=FALSE}
#onlyACC
pattern<-"Combined_data_sums_onlyACC.csv"
d1<-create_rowsum_lineplot(pattern)
p<-ggplot(d1, aes(x=Network, y=`Row Sum`,group=Method,color=Method)) + geom_line() + ggtitle("Row Sums Weight<sub>AUC=0</sub>, Weight<sub>ACC=1</sub> for Top 12 Methods across Networks")

p1<-ggplotly(p)
```

```{r plot 12, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot 13, include=FALSE}
#equal weights
pattern<-"Combined_data_sums_equal.csv"
d1<-create_rowsum_lineplot(pattern)
p<-ggplot(d1, aes(x=Network, y=`Row Sum`,group=Method,color=Method)) + geom_line() + ggtitle("Row Sums Weight<sub>AUC=0.5</sub>, Weight<sub>ACC=0.5</sub> for Top 12 Methods across Networks")

p1<-ggplotly(p)
```

```{r plot 13, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot 14, include=FALSE}


#AUC=0.3, ACC=0.7 weights
pattern<-"Combined_data_sums_37.csv"
d1<-create_rowsum_lineplot(pattern)
p<-ggplot(d1, aes(x=Network, y=`Row Sum`,group=Method,color=Method)) + geom_line() + ggtitle("Row Sums Weight<sub>AUC=0.3</sub>, Weight<sub>ACC=0.7</sub> for Top 12 Methods across Networks")

p1<-ggplotly(p)
```

```{r plot 14, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot 15, include=FALSE}

#AUC=0.7, ACC=0.3 weights
pattern<-"Combined_data_sums_73.csv"
d1<-create_rowsum_lineplot(pattern)
p<-ggplot(d1, aes(x=Network, y=`Row Sum`,group=Method,color=Method)) + geom_line() + ggtitle("Row Sums Weight<sub>AUC=0.7</sub>, Weight<sub>ACC=0.3</sub> for Top 12 Methods across Networks")
p1<-ggplotly(p)
```

```{r plot 15, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot 16, include=FALSE}
#onlyAUC
pattern<-"Combined_data_median_onlyAUC.csv"
d1<-create_median_lineplot(pattern)
p<-ggplot(d1, aes(x=Network, y=Median,group=Method,color=Method)) + geom_line() + ggtitle("Medians Weight<sub>AUC=1</sub>, Weight<sub>ACC=0</sub> for Top 12 Methods across Networks")
p1<-ggplotly(p)
```

```{r plot 16, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot 17, include=FALSE}
#onlyACC
pattern<-"Combined_data_median_onlyACC.csv"
d1<-create_median_lineplot(pattern)
p<-ggplot(d1, aes(x=Network, y=Median,group=Method,color=Method)) + geom_line() + ggtitle("Medians Weight<sub>AUC=0</sub>, Weight<sub>ACC=1</sub> for Top 12 Methods across Networks")
p1<-ggplotly(p)
```

```{r plot 17, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot 18, include=FALSE}
#equal weights
pattern<-"Combined_data_median_equal.csv"
d1<-create_median_lineplot(pattern)
p<-ggplot(d1, aes(x=Network, y=Median,group=Method,color=Method)) + geom_line() + ggtitle("Medians Weight<sub>AUC=0.5</sub>, Weight<sub>ACC=0.5</sub> for Top 12 Methods across Networks")

p1<-ggplotly(p)
```

```{r plot 18, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot 19, include=FALSE}
#AUC=0.3, ACC=0.7 weights
pattern<-"Combined_data_sums_37.csv"
d1<-create_median_lineplot(pattern)
p<-ggplot(d1, aes(x=Network, y=Median,group=Method,color=Method)) + geom_line() + ggtitle("Medians Weight<sub>AUC=0.3</sub>, Weight<sub>ACC=0.7</sub> for Top 12 Methods across Networks")
p1<-ggplotly(p)
```

```{r plot 19, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

```{r lineplot 20, include=FALSE}
#AUC=0.7, ACC=0.3 weights
pattern<-"Combined_data_sums_73.csv"
d1<-create_median_lineplot(pattern)
p<-ggplot(d1, aes(x=Network, y=Median,group=Method,color=Method)) + geom_line() + ggtitle("Medians Weight<sub>AUC=0.7</sub>, Weight<sub>ACC=0.3</sub> for Top 12 Methods across Networks")
p1<-ggplotly(p)
```

```{r plot 20, echo=FALSE}
ggplotly(p) %>%  layout(autosize = F, width = 900, height = 500)
```

